Do investors in clean energy ETFs herd? The role of climate risks

### 2025-09-24 alt_energy_herding_final.qmd
small changes

```{r functions}
source(here("Functions","flextable_word.R" ))
source(here("Functions","modelsummary_word.R" ))
source(here("Functions","modelplot_word.R" ))
source(here("Functions","borderlines.R" ))
source(here("Functions","fx_plot.R" ))

>>>>

```{r functions}
source(here("Functions","flextable_word.R" ))
source(here("Functions","modelsummary_word.R" ))
source(here("Functions","modelplot_word.R" ))
source(here("Functions","borderlines.R" ))
source(here("Functions","fx_plot.R" ))
```
